---
title: 'Homework 4: Bags, Forests, Boosts, oh my'
author: "Bassey Bassey"
date: "2/28/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libs, include=FALSE}
library(tree)
library(ISLR)
library(janitor)
library(caret)
library(stringr)
library(rsample)
library(boot)
library(tidyverse)
library(broom)
library(glmnet)
library(rpart)
library(rpart.plot)
library(partykit)
library(randomForest)
```



## Problem 1

Problem 7 from Chapter 8 in the text. To be specific, please use a sequence of
`ntree` from 25 to 500 in steps of 25 and `mtry` from 3 to 9 for by 1. 

## Answer 1

Since this was already answered in the last class (and since you said it wont be graded, I have not included it here)


## Problem 2

Problem 8 from Chapter 8 in the text. Set your seed with 9823 and split into 
train/test using 50\% of your data in each split. In addition to 
parts (a) - (e), do the following:

1. Fit a gradient-boosted tree to the training data and report the estimated 
test MSE. 
2. Fit a multiple regression model to the training data and report the 
estimated test MSE
3. Summarize your results. 

```{r}
attach(Carseats)
set.seed(9823)
df<- tbl_df(Carseats)
inTraining <- createDataPartition(df$Sales, p=.50, list= F)
training <- df[inTraining, ]
testing <- df[-inTraining, ]
```

B

```{r}

tree_carseats <- rpart::rpart(Sales ~ ., 
                              data = training,
                              control = rpart.control(minsplit = 20))
summary(tree_carseats)
prp(tree_carseats)
```

```{r}
plot(as.party(tree_carseats))
```

```{r}
pred_carseats = predict(tree_carseats, testing)
mean((testing$Sales - pred_carseats)^2)
```
 The test MSE is 2.8554
 
 
C


```{r}
fit_control <- trainControl(method = "repeatedcv",
                            number = 10, 
                            repeats = 10)
cv_tree_carseats <- train(Sales ~ ., 
                          data = training,
                          method = "rpart", 
                          trControl = fit_control)
plot(cv_tree_carseats)
```

```{r}
plot(as.party(cv_tree_carseats$finalModel))
```

```{r}
pred_carseats_1 = predict(cv_tree_carseats, testing)
mean((testing$Sales - pred_carseats_1)^2)
```

Pruning slightly reduces the test MSE to 2.832617

D


```{r}
bag_carseats <- randomForest(Sales ~ ., data = training, mtry = 10)
bag_carseats

test_preds <- predict(bag_carseats, newdata = testing)
carseats_test_df <- testing %>%
  mutate(y_hat_bags = test_preds,
         sq_err_bags = (y_hat_bags - Sales)^2)
mean(carseats_test_df$sq_err_bags)
```

The test error rate when using the bagging approach is further reduced to 2.303416


```{r}
importance(bag_carseats)
```

We can rightly conclude that “Price” and “ShelveLoc” are the two most important variables.

E

```{r}
rf_carseats <- randomForest(Sales ~ ., 
                            data = training,
                            mtry = 10)
rf_carseats

pred_carseats_3 = predict(rf_carseats, testing)
mean((testing$Sales - pred_carseats_3)^2)
```
The random forest MSE is 2.3171, just slightly higher than the MSE for the bagging approach.

```{r}
importance(rf_carseats)
```

We may rightly conclude here also, “Price” and “ShelveLoc” are the two most important variables.

Addtional Task

1.

```{r}
grid <- expand.grid(interaction.depth = c(1, 3), 
                    n.trees = seq(0, 2000, by = 100),
                    shrinkage = c(.01, 0.001),
                    n.minobsinnode = 10)
trainControl <- trainControl(method = "cv", number = 5)
gbm_carseats <- train(Sales ~ ., 
                      data = training, 
                      distribution = "gaussian", 
                      method = "gbm",
                      trControl = trainControl, 
                      tuneGrid = grid,
                      verbose = FALSE)
gbm_carseats
```

```{r}
plot(gbm_carseats)
```

```{r}
pred_carseats_4 = predict(gbm_carseats, testing)
mean((testing$Sales - pred_carseats_4)^2)
```

The MSE has further improved by being reduced to 1.558294


2. Fit a multiple regression model to the training data and report the  estimated test MSE
```{r}
lm_carseats <- lm(Sales ~.,
                  data = training)
lm_carseats

pred_carseats_final = predict(lm_carseats, testing)
mean((testing$Sales - pred_carseats_final)^2)
```
The test MSE here happens to be the best: 0.9196422

Summary of Mean Square Error

b- Regression Tree MSE: 2.8554
c- CV Pruned Regression Tree MSE: 2.8326
d- Bagged Random Forest MSE: 2.3034
e- Random Forest: 2.3171
f- Gradient Boosted Model: 1.5582
G- Multiple Regression Model: 0.9196
